Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-03-10 manuscript.tex
Add 'reminder' on how to generate 'redlined.md' [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/3c704477904acd1717b7d523cd8714280a4e457e.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/3c704477904acd1717b7d523cd8714280a4e457e/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/640042933

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...0dca14c42a639c9b0a7a75039e71d8cd74e41891}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/0dca14c42a639c9b0a7a75039e71d8cd74e41891/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/0dca14c42a639c9b0a7a75039e71d8cd74e41891}{habi/zmk-tooth-cohort-method-manuscript@0dca14c}
on March 10, 2021.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...3c704477904acd1717b7d523cd8714280a4e457e}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/3c704477904acd1717b7d523cd8714280a4e457e/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/3c704477904acd1717b7d523cd8714280a4e457e}{habi/zmk-tooth-cohort-method-manuscript@3c70447}
on March 10, 2021.
